---
title: "TITLE"
subtitle: "SUBTITLE"
date: "XX/XX/202X" 
output:
  pdf_document:
    latex_engine: pdflatex #xelatex #lualatex #pdflatex
    includes:
      in_header: ~/Dropbox/git/styles/style.sty
    #keep_tex:  true
  bookdown::pdf_book:
    citation_package: biblatex #natbib #biblatex
bibliography: ~/Dropbox/git/literature.bib
csl: ~/Dropbox/git/styles/my.csl
lang: de
fontsize: 12pt
---



<!-- title -->
\pagenumbering{gobble}


```{r, child=c('children/title.rmd')} 
```

<!-- comment ou at the end -->
\pagebreak 
\listoftodos
<!-- comment ou at the end -->
<!-- and comment in styles/style.sty/notes damit die notes verschwinden-->

\pagebreak 
\pagenumbering{roman}

\setstretch{1.5}
```{r, child=c('children/abstract.Rmd')} 
```


\setstretch{1} 
\pagebreak 
\listoffigures

\pagebreak 
\listoftables

\pagebreak 
\tableofcontents

\pagebreak 
\pagenumbering{arabic}




<!-- children -->
\setstretch{1.5} 
```{r, child=c('children/einleitung.Rmd', 'children/kapitel1.rmd','children/kapitel2.rmd','children/kapitel3.rmd','children/kapitel4.rmd', 'children/schluss.rmd')} 
```






\pagebreak  
# Literaturverzeichnis

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent

<div id="refs"></div>




\pagebreak 
\pagenumbering{gobble}
# Anhang {-} 


\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

```{r, child=c('children/apendix.Rmd')} 
```
